\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Albert Skalt} & \textbf{Email} : {allber971@gmail.com}\\
  \textbf{github:} \href{https://github.com/Arrias}{Arrias} & \textbf{Mobile} : +79094301315 \\
  \textbf{atcoder:} \href{https://atcoder.jp/users/Arrias}{Arrias} & \textbf{Telegram:} @Arrias \\
  \textbf{stepik:} \href{https://stepik.org/users/46148528}{Arrias} \\
  \textbf{codeforces:} \href{codeforces.com/profile/rapira}{rapira} \\
\end{tabular*}


\section{Profile}
A young programmer, who like olympiad in mathematics and computer science since high school. Interested in the development and improving of high-load systems. I am ready to study new technologies and their application. Now I am looking for an internship where I could prove myself and gain new experience.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Saint Petersburg State University}{Saint Petersburg, Russia}
      {Bachelor of Computer Science}{Sep. 2020 -- Present}
  \resumeSubHeadingListEnd

  
%-----------PROJECTS-----------------
\section{Selected projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Danverr/vk-app}{VK mini app "Mood"}}
      {A tracker of mood, anxiety and stress, where you can share your records and statistics with close friends. \textbf{JavaScript, React}.}
      
    \resumeSubItem{\href{https://github.com/Arrias/cppLabs/tree/main/hw_02}{Huffman Archiver}}
      {Archiver with canonical Huffman codes designed for fast and memory-efficient encoding and decoding of the big files. An university assignment written in \textbf{C++}.}
   
    \resumeSubItem{\href{https://github.com/Arrias/CompArchHW/tree/master/lab3}{Elf-file disassembler}}
      {Tool that builds text index and allows for fast queries on the analyzed data.  An university assignment written in \textbf{C++}.}
      
    \resumeSubItem{\href{https://github.com/Arrias/fpHomeWork} {Simply typed lambda calculus}}
      {A library that can $\beta$-reduce lambda terms and solve issues of their $\alpha\beta$-equivalence. The Hindley - Milner algorithm is implemented for type inference. An university assignment written in \textbf{Haskell}.}
      
    \resumeSubItem{\href{https://github.com/Arrias/mathlogic_normal_forms}{Formula Normalizer}}
      {The translator of formulas into normal forms: Negative Normal Form, Disjunctive Normal Form, Conjunctive Normal Form. An university assignment written in \textbf{Haskell}.}
      
      \resumeSubItem{Simple talk-chat implementation}
      {Chat on a local network with GUI. An university assignment written in \textbf{Kotlin, SQL}.}
  \resumeSubHeadingListEnd

%-----------ACADEMIC ACHIEVEMENTS-----------------
\section{Academic Achievements}
  \resumeSubHeadingListStart
  
  \resumeSubheading{\href{https://sesc.nsu.ru/upload/iblock/eb6/2019_3_inf_r.pdf}{All - Siberian Olympiad in Informatics}}{}
    {1st degree diploma in finals.}{2020}  
  
	\resumeSubheading{All Russian Olympiad in Informatics}{}
    {Finalist}{2019}  
  
    \resumeSubheading{\href{https://neerc.ifmo.ru/school/ioip/standings-2020.html}{Olympiad of schoolchildren in informatics and programming}}{}
    {1st degree diploma in finals.}{2020}
    
    \resumeSubheading{\href{https://mos-inf.olimpiada.ru/winners10-11-2020}{Moscow Olympiad in informatics}}{}
    {1st degree diploma in finals.}{2020}
    
    \resumeSubheading{Olympiad of schoolchildren of St. Petersburg
State University in informatics}{}
    {2nd degree diploma in finals.}{2020}
    
    \resumeSubheading{\href{https://olymp.hse.ru/data/2020/04/03/1556029378/\%D0\%98\%D0\%BD\%D1\%84\%D0\%BE\%D1\%80\%D0\%BC\%D0\%B0\%D1\%82\%D0\%B8\%D0\%BA\%D0\%B0\%2011.pdf}{All-Russian Olympiad of schoolchildren "The highest test" in informatics}}{}
    {2nd degree diploma in finals.}{2020}
    \resumeSubheading{All-Russian Team Olympiad of schoolchildren in programming}{}
    {3rd degree diploma in finals.}{2019, 2020}
    \resumeSubheading{Rucode command contest (div C/D)}{}
    {1st degree diploma in finals.}{2021}
    \resumeSubheading{\href{https://nerc.itmo.ru/archive/2021/northern/standings.html}{ICPC Northwestern Russia Regional Contest.}}{}
    {12th place.}{2021}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Kotlin, Haskell, JavaScript, SQL }
    }
     \item{
      \textbf{Technologies}{: PostgreSQL, ReactJS }
    }
  \resumeSubHeadingListEnd

%--------EDUCATION PROGRAMS--------
\section{Education programs}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Olympiad Preparation of Innopolis University}{}{parallels B+,A}{2018, 2019}
    \resumeSubheading
      {Algorithmic courses Tinkoff Generation}{}
      {parallel A'}{2019 -- 2020}  
           
        \resumeSubheading
      {Courses at the "Sirius" Educational Center
      }{}
      {olympiad informatics}{2018, 2019}  
           
  \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}